Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-23 analysis/normalized.Rmd
Variables

@@

useful_percent <- mean(bootstrap$t, na.rm = TRUE)

>>>>

What happens for the symbol with the default envir?

```{r}
var_sym_default_envir <- var_symb %>% filter(is.na(envir)) %>% count(src_ref, sort = TRUE)
```

Seems it was a bug: when the explicit argument was `parent.frame()`, it was counted as being the default argument (but it does not have the same semantics as a default argument or as an explicit one though!).

@@

#useful_percent <- mean(bootstrap$t, na.rm = TRUE)
useful_percent <- bootstrap$t0

### 2021-03-23 paper/main.tex
Add results of manual inspection of 20 sites with only values
Actual figure of manual imspection in the paper
Variables

\paragraph{Variables.}
The most common minimized expression is a variable.\footnote{An arithmetic expression with some variables and constant will also be normalized to \c{X}, i.e. a variable.} It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is used here to get the value of the variable in a non-local environment.

@@

\c{paste} concatenates strings and \eval will just return that string. \c{as.formula} can take a string and convert it to a formula; \eval is not needed here.

>>>>

\paragraph{Variables.}
The most common minimized expression is a variable.\footnote{An arithmetic expression with some variables and constant will also be normalized to \c{X}, i.e. a variable.} It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is often used here to get the value of the variable in a non-local environment. If we look only at the \emph{symbols} passed to \eval, the percentage of non-default environments goes up to \packageNbNonDefaultEnvirVariablesPercent.

@@

\c{paste} concatenates strings and \eval will just return that string. \c{as.formula} can take a string and convert it to a formula; \eval is not needed here. In 20 random sites among the ones with values, a conservative manual inspection showed that \packageUsefulValueEvalPercent of the sites  had a  legitimate reason to use \eval.
